A Data-Driven Framework for Neural Field Modelling

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
added bit about the varying sigmoid

\subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
To illustrate the effect of varying the 
Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy for the connectivity kernel for various parameters of the sigmoid. 
\subsubsection{Results for Varying the Sensor Kernel Width}

>>>>

\subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy (or RMSE) for the connectivity kernel for various parameters of the sigmoid, varying the slope, $\varsigma$, and the threshold, $\v_0$ . The size of the squares in the figure show the magnitude of the log of the error. The squares are black if the log of the error is negative (the RMSE is $<1$) and the squares are white of the log of the error is positive (the RMSE is $>1$). The largest black squares indicate the best performance and the largest white squares indicate the worst performance for the parameter combinations. 
\subsubsection{Results for Varying the Sensor Kernel Width}
